HaploQA vs. R/qtl2 Haplotype Reconstructions

### 2022-12-20 draft_report.Rmd
Update draft_report.Rmd

---
title: "Untitled"
output: html_document
date: '2022-10-18'
---

@@

```{r message=FALSE}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F)

@@

```{r}
plot_onegeno_test(do_results[['ph_geno']], do_results[['ph_geno_haploqa']], do_results[['map']], ind = 50, 
                          shift = TRUE, main = paste0('qtl2 - Geno-wide genotypes of individual ', 50),
                          sub = 'Left - qtl2, Right - HaploQA') 
```

@@

HaploQA:
  1. advantages: 
      a. Not a programming tool - people without relevant knowledge can still use the tool and perform haplotype reconstruction
      b. Works for all MUGA array-based genotyping data 
      c. Detailed and concise visualizations on web interface
  2. disadvantages:
      a. haplotype reports are not easy to access computationally
      b. source codes are also not easy to access computationally
      c. expensive to maintain at the organization's costs

R/qtl2: 
  1. advantages:
      a. fully accessible computationally
      b. capable of performing other genetic analysis
      c. currently maintained by developers
  2. disadvantages:
      a. algorithms is probability based, tends to bounce states when low-contribution founders are present
      b. does not scale well with large number of founders, run time increases exponentially 
      c. visualizations are less detailed and need to be generated on demand

#### 5. References
1. http://haploqa-dev.jax.org/help.html

>>>>

---
title: "HaploQA vs. R/qtl2 Haplotype Reconstructions"
output: html_document
date: '2022-12-16'
---

@@

```{r message=FALSE}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F)
```

@@

```{r}
plot_onegeno_test(do_results[['ph_geno']], do_results[['ph_geno_haploqa']], do_results[['map']], ind = 50, 
                          shift = TRUE, main = paste0('qtl2 - Geno-wide genotypes of individual ', 50),
                          sub = 'Left - qtl2, Right - HaploQA')

# remove DO from memory
```

@@

HaploQA:

  1. advantages:

      a. Not a programming tool - people without relevant knowledge can still use the tool and perform haplotype reconstruction

      b. Works for all MUGA array-based genotyping data

      c. Detailed and concise visualizations on web interface

  2. disadvantages:

      a. haplotype reports are not easy to access computationally

      b. source codes are also not easy to access computationally

      c. expensive to maintain at the organization's costs

R/qtl2:

  1. advantages:

      a. fully accessible computationally

      b. capable of performing other genetic analysis

      c. currently maintained by developers

  2. disadvantages:

      a. algorithms is probability based, tends to bounce states when low-contribution founders are present

      b. visualizations are less detailed and need to be generated on demand

      c. does not scale well with large number of founders, run time increases exponentially

      ![Genoprob runtime plot](/Users/linc/Desktop/genoprob_runtime.png)

#### 5. References

1. http://haploqa-dev.jax.org/help.html
